\documentclass[12pt,letterpaper]{amsart}

\sloppy

%\addtolength{\topmargin}{-70pt}
\addtolength{\textwidth}{60pt}
%\addtolength{\textheight}{120pt}
%\addtolength{\oddsidemargin}{-32pt}
\evensidemargin\oddsidemargin
\pagestyle{empty}
\pagenumbering{gobble}

\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}


%PACKAGES
\usepackage{geometry}               
\geometry{letterpaper}                   
\usepackage{graphicx}
\usepackage{amssymb}
%\usepackage{epstopdf}
\usepackage[all]{xy}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage[mathscr]{eucal}

\usepackage{rotating}
%\usepackage{enumerate}
%\usepackage{dsfont}
%\usepackage{mathtools}
%\usepackage{amsmath}
\usepackage{Trees}

%URL colors
\usepackage{color}
\definecolor{myurlcolor}{rgb}{0.6,0,0}
\definecolor{mycitecolor}{rgb}{0,0,0.8}
\definecolor{myrefcolor}{rgb}{0,0,0.8}
\usepackage{hyperref}
\hypersetup{colorlinks,
linkcolor=myrefcolor,
citecolor=mycitecolor,
urlcolor=myurlcolor}

\newtheorem{thm}{Theorem}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{fact}[thm]{Fact}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{example}[thm]{Example}
\newtheorem{defn}[thm]{Definition}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{sch}[thm]{Scholium}
\newcommand{\ctr}[1]{\begin{center} #1 \end{center}}
\newcommand{\oo}{\infty}
\newcommand{\al}[1]{\begin{align} #1 \end{align}}
\newcommand{\alx}[1]{\begin{align*} #1 \end{align*}}
\renewcommand{\AA}{\mathbf{A}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\CM}{\mathrm{CM}}
\newcommand{\gen}{\mathrm{gen}}
\newcommand{\maps}{\colon}
\newcommand{\tensor}{\otimes}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand {\tuple}[1]{\langle #1 \rangle}
\newcommand{\define}[1]{{\bf \boldmath{#1}}}

\begin{document}

\ctr{\large CURRENT AND PENDING SUPPORT}
\title{David I.\ Spivak}

\maketitle

David I.\ Spivak has no pending support.  His current support consists of 3 grants:

\begin{enumerate}
\item 
Project Title:  Category-Theoretic Approaches for the Analysis of Distributed Systems. \hfill \break
Source of Support: NASA. \hfill \break
Project Location: Massachusetts Institute of Technology. \hfill \break
Total Award Amount: \$300,000. \hfill \break
Starting Date: 06/01/2014.\hfill \break
Ending Date:  10/31/2014.\hfill \break
Person-months Per Year Committed to the Project: \hfill \break
Calendar: 0.833, Academic: 0.625, Summer: 0.208 

\vskip 1em
\item 
Project Title: Categorical Approach to Agent Interaction. \hfill \break
Source of Support: AFOSR. \hfill \break
Project Location: Massachusetts Institute of Technology.  \hfill \break
Starting Date: 12/01/2013. \hfill \break
Ending Date:  11/30/2018.\hfill \break
Person-months Per Year Committed to the Project: \hfill \break
Calendar: 1.500, Academic: 1.125, Summer: 0.375


\vskip 1em
\item 
Project Title: Pixel Matrices and Other Compositional Analyses of Interconnected Systems. \hfill \break
Source of Support: AFOSR. \hfill \break
Project Location: Massachusetts Institute of Technology. \hfill \break
Starting Date: 12/01/2016.\hfill \break
Ending Date:  11/30/2019.\hfill \break
Person-months Per Year Committed to the Project: \hfill \break
Calendar: 1.667, Academic: 1.250, Summer: 0.417


 \end{enumerate}




\end{document}
